Weather Data Integration and Assimilation System\\

### 2020-02-14 method/sec_3-microservice.tex
Updates from Overleaf
Complete performance analysis

\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries. These are the main endpoints to handle timeseries metadata which defines unique timeseries identifier based on the metadata values. As an example, if it needs to extend the system to store irregular grid data, then it should add another set of location endpoints for storing irregular grid location details.
\begin{itemize}
    \item parameter
    \begin{itemize}
        \item \texttt{GET /parameter} -- Get parameters
        \item \texttt{POST /parameter} -- Create parameter
        \item \texttt{PUT /parameter/id} -- Update parameter
        \item \texttt{DELETE /parameter/id} -- Delete parameter
    \end{itemize}
    \item timeStep
    \begin{itemize}
        \item \texttt{GET /timestep} -- Get TimeSteps
        \item \texttt{POST /timestep} -- Create TimeStep
        \item \texttt{PUT /timestep/id} -- Update TimeStep
        \item \texttt{DELETE /timestep/id} -- Delete TimeStep
    \end{itemize}
\dbc{Format others as above}
    \item location
    \begin{itemize}
        \item \texttt{GET /location} -- Get location points
        \item \texttt{POST /location} -- Create location point
        \item \texttt{PUT /location/id} -- Update location point
        \item \texttt{DELETE /location/id} -- Delete location point
        \item \texttt{GET /location/regular-grid} -- Get regular grids
        \item \texttt{POST /location/regular-grid} -- Create regular grid
        \item \texttt{PUT /location/regular-grid/id} -- Update regular grid
        \item \texttt{DELETE /location/regular-grid/id} -- Delete regular grid
    \end{itemize}
    \item timeseries
    \begin{itemize}
        \item \texttt{GET /timeseries} -- Get timeseries
        \item \texttt{POST /timeseries} -- Create timeseries
        \item \texttt{PUT /timeseries/id} -- Update timeseries
        \item \texttt{DELETE /timeseries/id} -- Delete timeseries
    \end{itemize}
\end{itemize}

@@

As it mentioned above, other than the timeseries metadata which is the core of the data system, other module endpoints start with the module name such as import, export and extension. This allows to add new module system if required.
For import and export modules, then follows by the data format. This provide the flexibility to integrate new data format modules.
Then the endpoint name ends with the data upload/insert data type. Data can upload as a single file with binary or multiple files with upload. Or in the body of the request as raw, and need to send the required headers has mentioned by particular module.
Thus the \acrshort{api} convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_DATA\_TYPE}} allows users to integrate new import or export modules into the system as well as add new data types.

>>>>

\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries. These are the main endpoints to handle timeseries metadata which defines unique timeseries identifier based on the metadata values. As an example, if it needs to extend the system to store irregular grid data, then it should add another set of location endpoints for storing irregular grid location details.
\begin{itemize}
    \item parameter
    \begin{itemize}
        \item \texttt{GET /parameter} -- Get parameters
        \item \texttt{POST /parameter} -- Create parameter
        \item \texttt{PUT /parameter/id} -- Update parameter
        \item \texttt{DELETE /parameter/id} -- Delete parameter
    \end{itemize}
    \item timeStep
    \begin{itemize}
        \item \texttt{GET /timestep} -- Get TimeSteps
        \item \texttt{POST /timestep} -- Create TimeStep
        \item \texttt{PUT /timestep/id} -- Update TimeStep
        \item \texttt{DELETE /timestep/id} -- Delete TimeStep
    \end{itemize}
\dbc{Format others as above}
\gkc{FIXED}
    \item location
    \begin{itemize}
        \item \texttt{GET /location} -- Get location points
        \item \texttt{POST /location} -- Create location point
        \item \texttt{PUT /location/id} -- Update location point
        \item \texttt{DELETE /location/id} -- Delete location point
        \item \texttt{GET /location/regular-grid} -- Get regular grids
        \item \texttt{POST /location/regular-grid} -- Create regular grid
        \item \texttt{PUT /location/regular-grid/id} -- Update regular grid
        \item \texttt{DELETE /location/regular-grid/id} -- Delete regular grid
    \end{itemize}
    \item timeseries
    \begin{itemize}
        \item \texttt{GET /timeseries} -- Get timeseries
        \item \texttt{POST /timeseries} -- Create timeseries
        \item \texttt{PUT /timeseries/id} -- Update timeseries
        \item \texttt{DELETE /timeseries/id} -- Delete timeseries
    \end{itemize}
\end{itemize}

@@

As it mentioned above, other than the timeseries metadata which is the core of the data system, other module endpoints start with the module name such as import, export and extension. This allows to add new module system if required.
For import and export modules, then follows by the data format. This provide the flexibility to integrate new data format modules.
Then the endpoint name ends with the data upload/insert data type. Data can upload as a single file with binary or multiple files with upload. Or in the body of the request as raw, and need to send the required headers has mentioned by particular module.
Thus the \acrshort{api} convention of \texttt{\hl{/MODULE/DATA\_FORMAT/DATA\_TYPE}} allows users to integrate new import or export modules into the system as well as add new data types.

### 2020-02-14 method/sec_4-db_struct.tex
Moved k8s to architectural decisions
Updated Microservice architecture
Complete performance analysis

\section{Hierarchical Database}

The database structure of WDIAS mainly depends on the key attributes of the timeseries. \hl{A brief summary of possible value for timeseries can be describe as below};
\dbc{Clerly mention why a hierarchical design is needed.}

@@

\paragraph{Location}-- Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS, namely:
\begin{itemize}
  \item \emph{Point locations}-- Contains a name which is human readable. lat and lon of the location on earth surface.
  \begin{lstlisting}[language=Python]
    {
        "locationId": "wdias-hanwella",
        "name": "Hanwella",
        "lat": 6.909722222,
        "lon": 80.08166667
    }
  \end{lstlisting}
  \dbc{Remove additional line.}

  \item \emph{Regular Grid locations} -- Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
  And the location of the first cell and the width and height of it.
  \begin{lstlisting}[language=Python]
      {
        "locationId": "wdias_kelani_basin",
        "description": "Kelani Basin",
        "rows": 120,
        "columns": 139,
        "geoDatum": "Kandawala",
        "gridFirstCell": {
            "firstCellCenter": {
                "x": 397074.0,
                "y": 504875.0
            },
            "xCellSize": 250.0,
            "yCellSize": 250.0
        }
    }
  \end{lstlisting}
  \item \emph{Irregular Grid locations} -- (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)
\end{itemize}

\paragraph{Parameter}
Parameter describe the variable measuring against a location. All parameters ahve a unique String identifier called as \textit{parameterId}. A parameter can be use in multiple locations.
While defining a parameter, there are three required fields which need to be provided such as variable, unit and \textit{parametertype}.
\begin{itemize}  
  \item \emph{Variable} -- Nature of the variable measuring. Example Precipitation, Temperature and WaterLevel etc
  \item \emph{Unit} -- metric unit of measuring
  \item \emph{Parameter Type} -- Should be one of Instantaneous, Accumulative, or Mean
  \begin{lstlisting}[language=Python]
    {
      "parameterId": "O.Precipitation",
      "variable": "Precipitation",
      "unit": "mm",
      "parameterType": "Instantaneous"
    }
  \end{lstlisting}
\end{itemize}

\subsubsection{Timeseries Type}
Timeseries Type can be combination of Source followed by category:
\begin{itemize}
  \item Sources - External or simulated
  \item Category - Historical or forecast
\end{itemize}
\dbc{Explain each with sufficient detail.}

\paragraph{Time Step}-- All Time Steps has an uniqie String identifier called as timeStepId. Unit should be one of Second, Minute, Hour, Day, Week, Month, Year, or NonEquidistant. One of multiplier or divider can be use to define the interval between each measurement.
\begin{lstlisting}[language=Python]
{
    "timeStepId": "each_min",
    "unit": "Minute",
    "multiplier": 1,
    "divider": 0
}
\end{lstlisting}

Among above key attributes; Location, Parameter and Time Step attributes are composite attributes. But each of them have an unique identifier.
Given that, a timeseries can uniquely indentify by moduleId, valueType, parameterId, locationId, timeseriesType and timeStepId.
\begin{lstlisting}[language=Python]
{
	"moduleId": "HEC-HMS",
	"valueType": "Scalar",
	"parameterId": "O.Precipitation",
	"locationId": "wdias_hanwella",
	"timeseriesType": "External_Historical",
	"timeStepId": "each_hour",
}
\end{lstlisting}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/microservice/hierarchical_database.jpg}
    \caption{Hierarchical database}
    \label{fi:hierarchical_database}
\end{figure}

\dbc{Fig. 3.6 needs a more meaningful title.}

WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \emph{Database per Service} in \cref{subse:database_per_service}.
Following chapters described the usage of databases in WDIAS and reason behind the selection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{rdbms}}
\label{subse:mysql}
\dbc{Needs a more meaningful Sec. title}

%There are lots of \acrshort{rdbms} available and for 
\acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
%SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
One instance of \acrshort{mysql} is using only by adapter-metadata service.
Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \cref{se:data_preprocess}.
\acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
As mentioned in \cref{subse:redis}, it uses \acrshort{redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
Other than MySQL, there are many open source databases can be used to replace the same functionality.
\dbc{First start with a brief discussion on why a RDBMS is needed}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Database}
\label{subse:influxdb}
Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{has higher number of usage and support. Database is written in Golang programming language, and} has higher performance, and has following supports;
\begin{itemize}
  \item Open timeseries DB with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}
Other than \acrshort{influxdb}, another database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
\acrshort{influxdb} can setup on a computer which will give the required performance. Going further, users can use commercial version of \acrshort{influxdb} in order to gain more performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrfull{netCDF}} 
\label{subse:netcdf}
\acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data formats that support creation, access, and sharing of array-oriented scientific data.
And it also has the support for parallel file access.
NetCDF is widely using in sciencetific domain due to it's capability of storing data in multi dementions easily and flexibility with storing many of the sciencetific data. \hl{
Python wrapper for NetCDF-C library using in the WDIAS system, and use by adapter-grid service.}

@@

\acrshort{wdias} is using \acrshort{mongodb} as the document-oriented databse, as it has the Geo searching capabilities.
\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general purpose, document-based, distributed database. And it supports:
\dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of EDIAS above.}
\begin{itemize}
  \item Supports query operations on geo-spatial data \cite{mongodbMongoDBManual}
  \item Clustering and Sharding available for scalability and reliability
\end{itemize}
\acrshort{mongodb} geo-spatial features are using for support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
If metadata not present in the adapter-query, if fetch data from the adapter-metadata, then indexed and cache in the \acrshort{mongodb}. Vise a versa, if new timeseries create in the adapter-metadata, it trigger an event to adapter-query to index the new timeseries.
In \cref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale the system.

>>>>

\section{\acrshort{wdias} Database Structure}
\label{se:db_struct}

In order to understand the underline design decisions of \acrshort{wdias} database structure, it need to deeply look into the weather data timeseries.
\paragraph{Timeseries}-- \emph{A timeseries is simply a series of data points ordered in time}. In weather domain, it interest in timeseries in perspective of observations to forecasting. Each timeseries, the data points can be form in different formats as well. For example, scalar (0D), vector (1D), grid (2D), and polygon (2D).

As per the above interpretation, a timeseries have data points ordered in time. Other than that, timeseries have other information which are known as \emph{timeseries metadata} which can use to uniquely identify one timeseries from another. As an example, a weather station can placed on a location and it can keep measure variables which are called as \emph{parameters} such as temperature, precipitation and wind direction which can produce different timeseries. Even we can use the location as metadata to identify the timeseries, that is not enough to separately identify the parameters. Thus we need to use set of attributes to uniquely identify a timeseries. In the next \cref{subse:timeseries_key_attributes}, we describe about key attributes which are using by the \acrshort{wdias} to uniquely identify a timeseries.

\dbc{Clearly mention why a hierarchical design is needed.}
\gkc{Added it after the \cref{subse:timeseries_key_attributes}}

@@

\paragraph{Location}-- Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS, namely:
\begin{itemize}
  \item \emph{Point locations}-- Contains a name which is human readable. lat and lon of the location on earth surface.
  \begin{lstlisting}[language=Python]
    {
        "locationId": "wdias-hanwella",
        "name": "Hanwella",
        "lat": 6.909722222,
        "lon": 80.08166667
    }
  \end{lstlisting}
  \dbc{Remove additional line.}
  \gkc{This space is adding by itemize. I applied in all the places. Could not find how to remove it. Otherwise, need to remove itemize.}
  \item \emph{Regular Grid locations} -- Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
  And the location of the first cell and the width and height of it.
  \begin{lstlisting}[language=Python]
      {
        "locationId": "wdias_kelani_basin",
        "description": "Kelani Basin",
        "rows": 120,
        "columns": 139,
        "geoDatum": "Kandawala",
        "gridFirstCell": {
            "firstCellCenter": {
                "x": 397074.0,
                "y": 504875.0
            },
            "xCellSize": 250.0,
            "yCellSize": 250.0
        }
    }
  \end{lstlisting}
  \item \emph{Irregular Grid locations} -- (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)
\end{itemize}

\paragraph{Parameter}
Parameter describe the variable measuring against a location. All parameters have a unique String identifier called as \textit{parameterId}. A parameter can be use in multiple locations.
While defining a parameter, there are three required fields which need to be provided such as variable, unit and \textit{parameterType}.
\begin{itemize}  
  \item \emph{Variable} -- Nature of the variable measuring. Example Precipitation, Temperature and Water Level etc
  \item \emph{Unit} -- metric unit of measuring
  \item \emph{Parameter Type} -- Should be one of Instantaneous, Accumulative, or Mean
  \begin{lstlisting}[language=Python]
    {
      "parameterId": "O.Precipitation",
      "variable": "Precipitation",
      "unit": "mm",
      "parameterType": "Instantaneous"
    }
  \end{lstlisting}
\end{itemize}

\subsubsection{Timeseries Type}
Timeseries Type can be redefine with the system setup. \acrshort{wdias} defined following types for during the setup. Timeseries type can be combination of source followed by category:
\begin{itemize}
  \item Sources - External or simulated. \emph{External} means whether timeseries is taken from external source, and \emph{simulated} means it generated by simulations of the users.
  \item Category - Historical or forecast. \emph{Historical} means whether timeseries have continuous data such as observations from a weather station. \emph{forecast} mean discrete set of timeseries data produce by forecasting.
\end{itemize}
\dbc{Explain each with sufficient detail.}
\gkc{FIXED}

\paragraph{Time Step}-- All Time Steps has an unique String identifier called as timeStepId. Unit should be one of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance. One of multiplier or divider can be use to define the interval between each measurement.
\begin{lstlisting}[language=Python]
{
    "timeStepId": "each_min",
    "unit": "Minute",
    "multiplier": 1,
    "divider": 0
}
\end{lstlisting}

Among above key attributes; Location, Parameter and Time Step attributes are composite attributes. But each of them have an unique identifier.
Given that, a timeseries can uniquely identify by moduleId, valueType, parameterId, locationId, timeseriesType and timeStepId.
\begin{lstlisting}[language=Python]
{
	"moduleId": "HEC-HMS",
	"valueType": "Scalar",
	"parameterId": "O.Precipitation",
	"locationId": "wdias_hanwella",
	"timeseriesType": "External_Historical",
	"timeStepId": "each_hour",
}
\end{lstlisting}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Even a timeseries consist of data points, the data for each data point can vary based on the valueType. For Scalar data point only consist from a single value. And Vector data point consist of two values such as magnitude and the direction of the Vector. But for Grid data a point can consist with multiple values.
In order to get the advantage of storing data efficiently, we can use set of different databases based on the advantage of using them for each valueType. Other than the valueType attribute, other attribute does not much impact on the data size.

Further it is will be difficult to search for the timeseries data, if those are stored over multiple data sources, and avoiding duplicates. Thus it add low overhead to have a single data source to look into while searching for the timeseries metadata. The load on above data source can reduce by using a caching mechanism. In order to support search queries with lower latency, it required to use an indexing for fast search for timeseries metadata. Further Geo based indexing is required in order to support Geo based search queries based on the locations.

With considering above facts, we can not achieve all of the benefits using one of database system available. Thus it required to have a database structure which is capable of proving all of above capabilities via combining together. According to the design principle of microservices architecture, we created microservice for each of the valueType with following the concept of Database per Service as described in the \emph{Database per Service} in \cref{subse:database_per_service}. In \cref{sebse:wdias_microservices} those microservices are group as \emph{adapters} which share an \acrshort{api} to interact with while keeping the persistent data private.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/microservice/wdias_database_structure.jpg}
    \caption{\acrshort{wdias} database structure}
    \label{fi:database_structure}
\end{figure}

\dbc{Fig. 3.6 needs a more meaningful title.}
\gkc{Updated. I think hierarchical database does not make sense in this case. May be that's why you asked for change few time, sir.}

\cref{fi:database_structure} shows the \acrshort{wdias} database structure.
Following sections describe the database structure of \acrshort{wdias} which respect to the design with more details on how is support the microservice architecture.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Metadata Storage}
\label{subse:mysql}
\dbc{Needs a more meaningful Sec. title}
\gkc{UPDATED}

As describe in above section, in order to reduce the overhead while searching for timeseries and handling duplicates, it required to have a timeseries metadata store. Since metadata consist of multiple key attributes, the data can be efficiently store using a \acrfull{rdbms}. This helps to store data without any duplicates and store the data with normalization. As an example, the parameter attribute can have one or two dozen of values. Using a \acrshort{rdbms}, those values can be store once and reuse with defining timeseries against location via reference.

\acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
One instance of \acrshort{mysql} is using only by adapter-metadata service.
Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \cref{se:data_preprocess}.
\acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
As mentioned in \cref{subse:redis}, it uses \acrshort{redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
Other than MySQL, there are many open source databases can be used to replace the same functionality.
\dbc{First start with a brief discussion on why a RDBMS is needed}
\gkc{ADDED}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Database}
\label{subse:influxdb}
Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{is using an unique database indexing algorithm in order to gain higher performance while storing timeseries data} when compared to other databases available. Also it has better support, higher number of usage and has following supports;
\begin{itemize}
  \item Open timeseries DB with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}
Other than \acrshort{influxdb}, another database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
\acrshort{influxdb} can setup on a computer which will give the required performance. Going further, users can use commercial version of \acrshort{influxdb} in order to gain more performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrfull{netCDF}}
\label{subse:netcdf}
\acrshort{netCDF} \cite{unidataUnidataNetCDF} is a self-describing, machine-independent data formats that support creation, access, and sharing of array-oriented scientific data.
And it also has the support for parallel file access.
NetCDF is widely using in scientific domain due to it has the capability of storing data in multi dimensions easily and flexibility with storing many of the scientific data. Due to its capability of storing scientific data efficiently, \acrshort{wdias} using it for storing the Grid data.

@@

\acrshort{wdias} is using \acrshort{mongodb} as the document-oriented databse, as it has the Geo searching capabilities.
\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general purpose, document-based, distributed database. And it supports:
\dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of WDIAS above.}
\gkc{Adding those details in \cref{se:high_level_design} may confuse the reader. At that point it didn't go through that much of details of the wdias. I added some justification at the end of \cref{subse:timeseries_key_attributes}. Let me know if we want to highlight it with a different section there.}
\begin{itemize}
  \item Supports query operations on geo-spatial data \cite{mongodbMongoDBManual}
  \item Clustering and Sharding available for scalability and reliability
\end{itemize}
\acrshort{mongodb} geo-spatial features are using for support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
If metadata not present in the adapter-query, if fetch data from the adapter-metadata, then indexed and cache in the \acrshort{mongodb}. Vise a versa, if new timeseries create in the adapter-metadata, it trigger an event to adapter-query to index the new timeseries.
In \cref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale the system.

### 2020-02-14 method/sec_5-data_preprocess.tex
Change all to \cref
Moved k8s to architectural decisions
Complete performance analysis

\section{Data Prepossessing}

The data imported via imported modules may have incorrect data, missing data and not compatible with directly feed into simulation modules. 
Thus it required to preprocess data before going to use in such cases. The WDIAS supports these capabilities via Extensions. Current system has
in build few extensions such as Interpolation, Transformation and Validation. Other than those, it possible to add more extensions as required.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{\hl{Weather data preprocessing}}
    \label{fi:weather_data_preprocessing}
\end{figure}

The WDIAS provides the support via in build simple generic mathematical function structure. Each extension is considering as a mathematical function which can take p 
number of input timeseries variables and output n number of timeseries variables. Other than that, at the time of processing the system can configure to provide
bind constant which can provide while configuring an extension. Which means, it is possible to change the behaviour of a existing function by providing different bind
constant at the time of creating new triggers for an extension.

@@

\subsection{Transformation}-- Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/transformation.jpg}
    \caption{\hl{Transformation}}
    \label{fi:transformation}
\end{figure}

\subsection{Validation}-- Checks for counting reliable, doubtful, unreliable, and missing values
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{\hl{Validation}}
    \label{fi:validation}
\end{figure}

\subsection{\hl{Extension API}}
In the WDIAS, it is possible to create new trigger for an extension via POST request to /extension endpoint.
\begin{lstlisting}[language=Python]
{
    "extensionId": "",
    "extension": "Interpolation/Transformation/Validation",
    "function": "",
    "variables": [
        {
            "variableId": "",
            "metadata/metadtaIds": {
            }
        }
    ],
    "inputVariables": [],
    "outputVariables": [],
    "trigger": [
        {
            "trigger_type": "OnChange/OnTime",
            "trigger_on": []
        }
    ],
    "options": {
    }
}
\end{lstlisting}
\begin{itemize}
    \item extensionId -- An unique identifier for new extension trigger. Should be unique among all extensions.
    \item extension -- The main extension category which is responsible for handling the extension with extracting data required and storing the output. Interpolation/Transformation/Validation support for the moment.
    \item function -- Name of the microservice which is handling the input to output mapping. Fn() function in the Figure \ref{fi:weather_data_preprocessing}.
    \item variables -- Array timeseries mapping to variables. Multiple variables can be define with metadata or metadataIds of timeseries. Can be use same variable on inputVariables and outputVariables below.
    \item inputVariables -- Timeseries that need to be provide into the function
    \item outputVariables -- Timeseries that output from the function
    \item trigger -- Type of trigger for the extension. Should be one of OnTime or OnChange.
    \begin{itemize}
        \item trigger -- OnChange
        \item trigger\_on -- List of timeseries to listen on change and trigger the extension
    \end{itemize}
    \begin{itemize}
        \item trigger -- OnTime
        \item trigger\_on -- List of schedules that need to be trigger the extension in cronjob string format
    \end{itemize}
    \item options -- Bind Constant which is bind at the time of creating new extension trigger and pass on triggering the extension.
\end{itemize}

\subsubsection{Extension Handler}
Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on subscribed extension trigger's OnChange timeseries.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{Extension handler.}
    \label{fi:extension_handler}
\end{figure}

\hl{In further elaboration,} when new data imported into one of adapter-scalar or adapter-vector, those notify the extension-handler. Then extension handler check whether there is any extension subscribed for particular timeseries, and trigger it via triggering an event on particular extensions.

>>>>

\section{Data Prepossessing}
\label{se:data_preprocess}

The data imported via imported modules may have incorrect data, missing data and not compatible with directly feed into simulation modules. 
Thus it required to preprocess data before going to use in such cases. The WDIAS supports these capabilities via Extensions. Current system has
in build few extensions such as Interpolation, Transformation and Validation. Other than those, it possible to add more extensions as required.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{\hl{Generic mathematical function model for weather data preprocessing}}
    \label{fi:weather_data_preprocessing}
\end{figure}

The WDIAS provides the support via in build simple generic mathematical function model. Each extension is considering as a mathematical function which can take p 
number of input timeseries variables and output n number of timeseries variables. Other than that, at the time of processing the system can configure to provide
bind constant which can provide while configuring an extension. Which means, it is possible to change the behaviour of a existing function by providing different bind
constant at the time of creating new triggers for an extension.

@@

\subsection{Transformation}-- Simple arithmetic manipulation, Time interval transformation and Shifting the series in time Specific hydro-meteorological transformation such as stage discharge relationships.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/transformation.jpg}
    \caption{\hl{Time interval transformation.}}
    \label{fi:transformation}
\end{figure}

\subsection{Validation}-- Checks for counting reliable, doubtful, unreliable, and missing values
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{\hl{Timeseries data validation against set of rules.}}
    \label{fi:validation}
\end{figure}

\subsection{\hl{Data Preprocessing API}}
In the WDIAS, it is possible to create new trigger for an extension via POST request to /extension endpoint.
\begin{lstlisting}[language=Python]
{
    "extensionId": "",
    "extension": "Interpolation/Transformation/Validation",
    "function": "",
    "variables": [
        {
            "variableId": "",
            "metadata/metadtaIds": {
            }
        }
    ],
    "inputVariables": [],
    "outputVariables": [],
    "trigger": [
        {
            "trigger_type": "OnChange/OnTime",
            "trigger_on": []
        }
    ],
    "options": {
    }
}
\end{lstlisting}
\begin{itemize}
    \item extensionId -- An unique identifier for new extension trigger. Should be unique among all extensions.
    \item extension -- The main extension category which is responsible for handling the extension with extracting data required and storing the output. Interpolation/Transformation/Validation support for the moment.
    \item function -- Name of the microservice which is handling the input to output mapping. Fn() function in the \cref{fi:weather_data_preprocessing}.
    \item variables -- Array timeseries mapping to variables. Multiple variables can be define with metadata or metadataIds of timeseries. Can be use same variable on inputVariables and outputVariables below.
    \item inputVariables -- Timeseries that need to be provide into the function
    \item outputVariables -- Timeseries that output from the function
    \item trigger -- Type of trigger for the extension. Should be one of OnTime or OnChange.
    \begin{itemize}
        \item trigger -- OnChange
        \item trigger\_on -- List of timeseries to listen on change and trigger the extension
    \end{itemize}
    \begin{itemize}
        \item trigger -- OnTime
        \item trigger\_on -- List of schedules that need to be trigger the extension in cronjob string format
    \end{itemize}
    \item options -- Bind Constant which is bind at the time of creating new extension trigger and pass on triggering the extension.
\end{itemize}

\subsubsection{Extension Handler}
Extension Handler is responsible for triggering the correct Extension with metadata when there is any change on subscribed extension trigger's \emph{OnChange} timeseries.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/data_preprocess/validation.jpg}
    \caption{Extension handler.}
    \label{fi:extension_handler}
\end{figure}

\hl{As an example,} when new data imported into one of adapter-scalar or adapter-vector, those notify the extension-handler. Then extension handler check whether there is any extension subscribed for particular timeseries, and trigger it via triggering an event on particular extensions.

### 2020-02-14 summary/sec_1-conclusions.tex
Complete performance analysis

To enhance the accuracy of the weather prediction, it is essential to provide reliable and timely weather data for \acrshort{nwm}. Even though there are many data integration systems, most of them are proprietary or close sourced. Which means for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized. \hl{Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. Also most of existing systems are not up to date with the cloud computing technologies, or bias to some research community.}
/dbc{Look some of the changes in abstract and revise this para. However, don't repeat the same from abstract.}

>>>>

To enhance the accuracy of the weather prediction, it is essential to provide reliable and timely weather data for \acrshort{nwm}. Even though there are many data integration systems, most of them are proprietary or close sourced. Which means for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized. \hl{Throughout the operations and maintenance, it is required to get support with paying lots of charges, and difficult to debug into a closed source system without maintenance support from the vendors. Also most of existing systems are not up to date with the cloud computing technologies, or bias to some research community.}

/dbc{Look some of the changes in abstract and revise this para. However, don't repeat the same from abstract.}

### 2020-02-14 summary/sec_2-research_limitations.tex
Complete performance analysis

\section{Research Limitations}
This section discussed about the lacking features in the \acrshort{wdias}, and some of the improvement that can add for improve the performance and usability of the system.

@@

\dbc{Need a new section for Conclusions.}

>>>>

\section{Research Limitations}
\gkc{Previously you asked to rename this section. Why can't it have the title of \emph{Future Work}. There are some of the requirements that can be done for the system, in order to gain more of it. Which part is misleading?}
This section discussed about the lacking features in the \acrshort{wdias}, and some of the improvement that can add for improve the performance and usability of the system.

@@

\dbc{Need a new section for Conclusions.}
\gkc{It did not make sense for me to adding another section as Conclusion. We already add a \cref{se:summary_conclusion} above. Do we need to rearrange the content of this Chapter? No point of adding another section with repeating the same content. May be I didn't understand your suggestion here.}
\gkc{DO we need to move the \cref{se:discussion} here? Normally where should we include the analysis of observations?}
